Ground state energy of quantum dots using the coupled cluster method

### 2018-05-09 project_2/article/article.tex
Add FIXME
Use u instead of W and w

@@

\section{Theory}
    In this project we will study a system of $N$ interacting electrons. We will
    be looking at a Hamiltonian consisting of a one-body and a two-body part.
    The one-body part is given by
    \begin{align}
        h(\vf{r}_i)
        &= -\half\nabla_i^2 + \half\omega^2 \vf{r}_i^2,
    \end{align}
    where we use natural units $\hbar = c = e = 1$ and set the mass to unity.
    % Why not write $\hbar = c = e = m = 1$?
    The two-body part is the Coulomb interaction potential.
    \begin{align}
        w(\vf{r}_i, \vf{r}_j)
        &= \frac{1}{\abs{\vf{r}_i - \vf{r}_j}}.
    \end{align}
    We thus get the total Hamiltonian
    \begin{align}
        H &= h + W
        =
        \sum_{i = 1}^N h(\vf{r}_i) + \sum_{i < j}^N w(\vf{r}_i, \vf{r}_j),
    \end{align}
    where $h$ is the full one-body operator and $W$ the full two-body
    operator, i.e., over the entire system.  Working in a basis of $L$ single
    particle functions, $\{\ket{p}\}_{p = 1}^L$. We define the reference Slater
    determinant as
    \begin{align}
        \ket{\Phi_0} &\equiv \ket{1, 2, \dots, N},
    \end{align}
    i.e., a tensorproduct of the $N$ first single particle functions, $\ket{i}$,
    of the system. We call these single particle functions \emph{occupied} as
    they are contained in the Slater determinant.  We will denote the occupied
    indices with $i, j, k, l, \dots \in \{1, \dots, N\}$, the \emph{virtual}
    states with $a, b, c, d, \dots \in \{N + 1, \dots, L\}$ and general indices
    with $p, q, r, s, \dots \in \{1, \dots, L\}$. In terms of sets of basis
    functions we can write this as
    \begin{align}
        \{\ket{p}\}_{p = 1}^L
        = \{\ket{i}\}_{i = 1}^N
        \cup
        \{\ket{a}\}_{a = N + 1}^L,
    \end{align}
    i.e., the general indexed states consists of both occupied and virtual
    states. Note that the single particle functions are orthonormal, i.e.,
    \begin{align}
        \braket{p}{q} = \delta_{pq}.
    \end{align}
    We can construct other Slater determinants in this basis by exciting
    or relaxing the reference determinant. A general excitation is labeled
    $\ket{\Phi_{ij\dots}^{ab\dots}}$ which means that we have removed the single
    particle functions with indices $i, j, \dots$ from the reference and added
    $a, b, \dots$. Note that
    \begin{align}
        \braket{\Phi^{ab\dots}_{ij\dots}}{\Phi_0} = 0,
        \label{eq:excited_overlap}
    \end{align}
    for any excitation.

    \subsection{Second quantization}
        Employing the creation operators, $\acr{p}$, and the destruction
        operators, $\ade{p}$, we can write the Hamiltonian as
        \begin{align}
            H
            &=
            \sum_{pq}h_{q}^{p}\acr{p}\ade{q}
            + \frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}\acr{p}\acr{q}\ade{s}\ade{r},
        \end{align}
        where the sums are general indices over all $L$ basis states and the
        matrix elements are defined as
        \begin{gather}
            h^{p}_{q} \equiv \bra{p}h\ket{q}, \\
            \bra{pq}\ket{rs} \equiv \bra{pq}w\ket{rs} - \bra{pq}w\ket{sr}.
        \end{gather}
        Note that we use the chemists notation to label the antisymmetric matrix
        elements.

@@

\appendix
\section{The normal ordered Hamiltonian}
    When constructing the normal ordered Hamiltonian we use Wick's theorem to
    write the one-body, $h$, and the two-body, $W$, operators onto a normal
    ordered form. Specifically we define the normal ordered form in terms of the
    \emph{Fermi vacuum}\footnote{Fermi vacuum defines the reference state, i.e.,
    $\kslat$, as the vacuum.}. That is, an operator on normal ordered form
    destroys the reference Slater determinant.

@@

        W

>>>>

% FIXME: Replace the two-body matrix elements in bra-ket notation with u-tensor.

@@

\section{Theory}
    In this project we will study a system of $N$ interacting electrons. We will
    be looking at a Hamiltonian consisting of a one-body and a two-body part.
    The one-body part is given by
    \begin{align}
        h(\vf{r}_i)
        &= -\half\nabla_i^2 + \half\omega^2 \vf{r}_i^2,
    \end{align}
    where we use natural units $\hbar = c = e = 1$ and set the mass to unity.
    % Why not write $\hbar = c = e = m = 1$?
    The two-body part is the Coulomb interaction potential.
    \begin{align}
        u(\vf{r}_i, \vf{r}_j)
        &= \frac{1}{\abs{\vf{r}_i - \vf{r}_j}}.
    \end{align}
    We thus get the total Hamiltonian
    \begin{align}
        H &= h + u
        =
        \sum_{i = 1}^N h(\vf{r}_i) + \sum_{i < j}^N u(\vf{r}_i, \vf{r}_j),
    \end{align}
    where $h$ is the full one-body operator and $u$ the full two-body
    operator, i.e., over the entire system.  Working in a basis of $L$ single
    particle functions, $\{\ket{p}\}_{p = 1}^L$. We define the reference Slater
    determinant as
    \begin{align}
        \ket{\Phi_0} &\equiv \ket{1, 2, \dots, N},
    \end{align}
    i.e., a tensorproduct of the $N$ first single particle functions, $\ket{i}$,
    of the system. We call these single particle functions \emph{occupied} as
    they are contained in the Slater determinant.  We will denote the occupied
    indices with $i, j, k, l, \dots \in \{1, \dots, N\}$, the \emph{virtual}
    states with $a, b, c, d, \dots \in \{N + 1, \dots, L\}$ and general indices
    with $p, q, r, s, \dots \in \{1, \dots, L\}$. In terms of sets of basis
    functions we can write this as
    \begin{align}
        \{\ket{p}\}_{p = 1}^L
        = \{\ket{i}\}_{i = 1}^N
        \cup
        \{\ket{a}\}_{a = N + 1}^L,
    \end{align}
    i.e., the general indexed states consists of both occupied and virtual
    states. Note that the single particle functions are orthonormal, i.e.,
    \begin{align}
        \braket{p}{q} = \delta_{pq}.
    \end{align}
    We can construct other Slater determinants in this basis by exciting
    or relaxing the reference determinant. A general excitation is labeled
    $\ket{\Phi_{ij\dots}^{ab\dots}}$ which means that we have removed the single
    particle functions with indices $i, j, \dots$ from the reference and added
    $a, b, \dots$. Note that
    \begin{align}
        \braket{\Phi^{ab\dots}_{ij\dots}}{\Phi_0} = 0,
        \label{eq:excited_overlap}
    \end{align}
    for any excitation.

    \subsection{Second quantization}
        Employing the creation operators, $\acr{p}$, and the destruction
        operators, $\ade{p}$, we can write the Hamiltonian as
        \begin{align}
            H
            &=
            \sum_{pq}h_{q}^{p}\acr{p}\ade{q}
            + \frac{1}{4}\sum_{pqrs}\bra{pq}\ket{rs}\acr{p}\acr{q}\ade{s}\ade{r},
        \end{align}
        where the sums are general indices over all $L$ basis states and the
        matrix elements are defined as
        \begin{gather}
            h^{p}_{q} \equiv \bra{p}h\ket{q}, \\
            \bra{pq}\ket{rs} \equiv \bra{pq}u\ket{rs} - \bra{pq}u\ket{sr}.
        \end{gather}
        Note that we use the chemists notation to label the antisymmetric matrix
        elements.

@@

\appendix
\section{The normal ordered Hamiltonian}
    When constructing the normal ordered Hamiltonian we use Wick's theorem to
    write the one-body, $h$, and the two-body, $u$, operators onto a normal
    ordered form. Specifically we define the normal ordered form in terms of the
    \emph{Fermi vacuum}\footnote{Fermi vacuum defines the reference state, i.e.,
    $\kslat$, as the vacuum.}. That is, an operator on normal ordered form
    destroys the reference Slater determinant.

@@

        u
